### 2018-12-09 supplements/KineticsTable/kinetics_table.tex
included all comments from Marc

\subsection*{Amount of enzymes and import rates}
The total enzyme concentration was set to 10 for all enzymes except NamPT and NMNAT, for which the concentration was set to 100. Concentration of potential co-substrate was assumed to be constant and not-limiting for the reaction. Thus being implicitly represented by turnover rates measured at saturating conditions for the cosubstrate. Nam import rates for iport into the system was set to 0.1 $\mu$M/ls for all simulations. For the two compartment simulation compartmentsize was equal to ... for both compartments. The Nam import rates were set to 100/s for both compartments. The amount of NADA present was set to 100. Thus equal to the amount of NamPT used.

>>>>

\subsection*{Amount of enzymes and import rates}
The total enzyme concentration was set to 10 times the scaling factor, for all enzymes except NamPT and NMNAT, for which the concentration was set to 100 times the scaling factor. As enzyme concentrations here have an arbitrary unit a scaling factor of 0.1$\mu$M  was applied to all enzymatic reactions to achieve consumption rates that are in the range of reported values  \cite{Liu2018}. Concentration of potential co-substrates were assumed to be constant and not-limiting for the reaction. Thus being implicitly represented by maximal velocities consiting of total enzyme concentration times tunrover rates. Nam import rates for import into the system was set to 0.1 $\mu$M/s for all simulations, being in the range meassured for Nam uptake in mammalian cells \cite{Namuptake}. For the two compartment simulation compartmentsize was equal to ... for both compartments. The Nam import rates were set to 100/s for both compartments. The amount of NADA present was set to 100. Thus equal to the amount of NamPT used.
